Monitoring misinformation related interventions by Facebook, Twitter and YouTube: methods and illustration.

### 2022-04-27 article/draft.tex
typo

Furthermore, mainstream platforms are increasingly engaging in editorial-like tasks by implementing targeted policies to insure that each platform's rules are not violated. Community guidelines of Facebook, Twitter and YouTube can be summarized in a handful of categories, regarding safety, privacy and authenticity; which include sub-categories such as violence, terrorism, child sexual exploitation, abuse, harassment, hateful conduct, suicide or self-harm, illegal or regulated goods and services, platform manipulation and spam (see Appendix \ref{links} for references). While specific to each platform, the previously cited categories correspond in most cases to well defined concepts that fall into legal frameworks in many countries, unlike misinformation. The intricacies of constructing a legal framework for misinformation arises from the difficulty of identifying and qualifying a piece of online content as false or misleading, among an overwhelming quantity of daily produced content, without infringing existing laws.\footnote{See \href{https://www.poynter.org/ifcn/anti-misinformation-actions/}{A guide to anti-misinformation actions around the world} on the website of Poynter Institute.} In particular, a number of recent studies point towards the idea that misinformation is a small subset of the total supply of information on online social networking platforms (e.g. Grinberg et al. (2019)~\cite{grinberg} and Broniatowski et al. (2020)~\cite{broniatowski}). Yet, this seemingly small subset is generating great concern in traditional media and in society in a broader sense. \footnote{For example see the February 2020 \href{https://www.who.int/director-general/speeches/detail/munich-security-conference}{speech} of the Director General of the WHO at the Munich Security Conference, where he says ``But we’re not just fighting an epidemic; we’re fighting an infodemic.'' Furthermore, the European commission recognizes the spread of online disinformation as a problem and has put together in 2018 a \href{https://digital-strategy.ec.europa.eu/en/policies/code-practice-disinformation}{Code of practice on Disinformation}, which is a set of self-regulatory standards to fight disinformation.}

>>>>

Furthermore, mainstream platforms are increasingly engaging in editorial-like tasks by implementing targeted policies to insure that each platform's rules are not violated. Community guidelines of Facebook, Twitter and YouTube can be summarized in a handful of categories, regarding safety, privacy and authenticity; which include sub-categories such as violence, terrorism, child sexual exploitation, abuse, harassment, hateful conduct, suicide or self-harm, illegal or regulated goods and services, platform manipulation and spam (see Appendix \ref{links} for references). While specific to each platform, the previously cited categories correspond in most cases to well defined concepts that fall into legal frameworks in many countries, unlike misinformation. The intricacies of constructing a legal framework for misinformation arises from the difficulty of identifying and qualifying a piece of online content as false or misleading, among an overwhelming quantity of daily produced content, without infringing existing laws.\footnote{See \href{https://www.poynter.org/ifcn/anti-misinformation-actions/}{A guide to anti-misinformation actions around the world} on the website of Poynter Institute.} In particular, a number of recent studies point towards the idea that misinformation is a small subset of the total supply of information on online social networking platforms (e.g. Grinberg et al. (2019)~\cite{grinberg} and Broniatowski et al. (2020)~\cite{broniatowski}). Yet, this seemingly small subset is generating great concern in traditional media and in society in a broader sense.\footnote{For example see the February 2020 \href{https://www.who.int/director-general/speeches/detail/munich-security-conference}{speech} of the Director General of the WHO at the Munich Security Conference, where he says ``But we’re not just fighting an epidemic; we’re fighting an infodemic.'' Furthermore, the European commission recognizes the spread of online disinformation as a problem and has put together in 2018 a \href{https://digital-strategy.ec.europa.eu/en/policies/code-practice-disinformation}{Code of practice on Disinformation}, which is a set of self-regulatory standards to fight disinformation.}
